R Notebook

### 2021-06-07 FEM_R/dfly_detailed_output.Rmd
Trying some big changes for ROC curves and calculated dflys in an R script

theme('minimal')
```

Setup is complete (including the working directory), so let's read in some of the data files.

@@

# generate flag for initial wave with disease and year died (if known)
new <- cohort %>%
          group_by(hhidpn, mcrep, year) %>%

@@

>>>>

theme('minimal')
rm(workingDir)
```

Setup is complete, so let's read in some of the data files.

@@

# generate flag for initial wave with disease and year died (if known)
new <- cohort %>%
          group_by(hhidpn, mcrep) %>%
          arrange(year, .by_group = TRUE) %>%
          mutate(hearte_init = min(year[hearte == 1]), hearte_died = max(year[hearte == 1])) %>%
          mutate(lunge_init = min(year[lunge == 1]), lunge_died = max(year[lunge == 1]))

new$hearte_init[is.infinite(new$hearte_init)] <- 0
new$hearte_died[is.infinite(new$hearte_died)] <- 0
new$lunge_init[is.infinite(new$lunge_init)] <- 0
new$lunge_died[is.infinite(new$lunge_died)] <- 0

@@

# Using output from stata script treatment_on_treated.do or some version of it
